---
title: "patter-cheatsheet-code-blocks"
output: word_document
date: "2024-03-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Initialisation

A. Load & attach `patter`:
```{r}
library(patter)
```

B. Initialise `patter`:
```{r}
julia_connect(JULIA_HOME, ...)
```

# Inputs

## Real data

A. Study area:

```{r}
map <- dat_gebco()
set_map(map)
```

B. Example datasets:
```{r}
?`datasets-mefs`
```

C. Data assembly:
```{r}
assemble_*()
```

## Abstract types

A. Define `State`
```{r}
?State
```

B. Define movement model
```{r}
?ModelMove
```

B. Define observation model(s):
```{r}
?ModelObs
```

## Simulate data

A. Simulate receiver array(s):
```{r}
sim_array(.map,
          .timeline,
          .arrangement, 
          .n_receiver, 
          ...)
```

B. Simulate movement path(s):
```{r}
sim_path_walk(.map,
              .timeline,
              .state, 
              .model_move, 
              ...)
```

C. Simulate observation(s):
```{r}
sim_observations(.timeline, 
                 .model_obs, 
                 ...)
```

# Algorithms

## Filter

A. Run forward filter:
```{r}
pf_filter(.map, 
          .timeline, 
          .state, 
          .yobs,
          .model_move, 
          .model_obs, ...)
```

B. (optional) Run backward filter:
```{r}
pf_filter(..., 
          .direction = "backward")
``` 

## Smoother

A. Run forward & backward filter

B. Run two-filter smoother:
```{r}
pf_smoother_two_filter()
```

## Utilities


# Outputs

A. Visualise particle histories:
```{r}
pf_plot_*(.map, 
          .coord, ...)
```

B. Map UD(s):
```{r}
map_pou(.map, 
        .coord, ...)
map_dens(.map,
         .coord, ...)
```

C. Map home ranges:
```{r}
map_hr_*(.map, ...)
```

## Paths 

# To Do

* specify Julia threads from R
